Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need the codomain when evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -JS
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -JS
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -JS
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
        \\---\\
        The answer you put in the text is too vague. -JS
        }
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

>>>>

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need to compute identity hypercoercion for the codomain when 
evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -JS
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -JS
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -JS
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
        \\---\\
        The answer you put in the text is too vague. -JS
        \\---\\
        Fixed. -KC}
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

\begin{proposition}[\lazyUD\ hypercoercions form a monoid]
	For all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{proposition}
